### 2023-02-09 documentation/paper.tex
Finish

%-------------------------------------------------------------------------
\begin{abstract}
Compared to cameras built specifically for photography, cameras used in smartphones 
suffer from constructional limitations that restrict image quality, such as smaller 
sensors and pixels, shorter focal lengths and smaller apertures. To compensate for 
these limitations, techniques from computational photography are used, whereby many 
current improvements are based on the processing of several similar images of the same 
scene - so-called image bursts. In the course of this work, an existing implementation 
of a burst processing pipeline was examined more closely and applied to example bursts 
from mobile and DSLR cameras. In order to enable as many people as possible to 
experiment with this implementation, it was adapted in such a way that it can be 
used platform-independently. Even if performance and operation are not sufficient 
to be used in a business context, it is suitable for an introduction to and initial 
experimentation with burst processing.
\end{abstract}

>>>>

%-------------------------------------------------------------------------
\begin{abstract}
Compared to cameras built specifically for photography, cameras used in smartphones 
suffer from constructional limitations that restrict image quality, such as smaller 
sensors and pixels, shorter focal lengths as well as smaller apertures. To compensate for 
these limitations, techniques from computational photography are used, whereby many 
current improvements are based on the processing of several similar images of the same 
scene - so-called image bursts. In the course of this work, an existing implementation 
of a burst processing pipeline was examined more closely and applied to example bursts 
from mobile and DSLR cameras. In order to enable as many people as possible to 
experiment with this implementation, it was adapted in such a way that it can be 
used platform-independently. Even if performance and operation are not sufficient 
to be used in a business context, it is suitable for an introduction to and initial 
experimentation with burst processing.
\end{abstract}
